The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 SI.tex
Fix missing cross-ref links

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
  \caption{Validation the linear relation between \textbf{a}
    $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
    database, corresponding to Figure 3b and 3c in main text.}
  \label{fig:gpaw-alpha-relation}
\end{figure}

@@

A common approach for describing the bulk dielectric function of bulk
semiconductors is via the Lorentz oscillator model, where the
dielectric function is dominated by the plasma frequencies
$\omega_{\mathrm{3D}}^{\mathrm{p}}$ and bandgap $E_{\mathrm{g}}$ of
individual oscillators \cite{ketterson_physics_2016}. At zero optical
frequency and the static limit, the dielectric constant for single
oscillator is:
\begin{equation}
  \label{eq:eps-plas-3D}
  \varepsilon_{\mathrm{3D}} = 1 +
  \frac{\hbar^{2} (\omega_{\mathrm{3D}}^{\mathrm{p}})^{2}}{E_{\mathrm{g}}^{2}}
\end{equation}
where
$\omega_{\mathrm{3D}}^{\mathrm{p}} = {\displaystyle \sqrt{\frac{e^{2}
      n_{\mathrm{3D}}}{\varepsilon_{0} m_{e}}}}$, where
$n_{\mathrm{3D}}$ is the 3D number density of valence
electrons. Combine Eq. \ref{eq:eps-plas-3D} with Eq. 3 in main text,
we get:
\begin{equation}
  \begin{aligned}
  \label{eq:alpha-plas}
  \alpha_{\mathrm{2D}}^{\parallel} &= \frac{e^{2} n_{\mathrm{3D}} L}{m_{e} E_{\mathrm{g}}^{2}} \\
  &= \frac{e^{2} n_{\mathrm{2D}}}{m_{e} E_{\mathrm{g}}^{2}} \\
  &= \varepsilon_{0} \frac{\hbar^{2}
    (\omega_{\mathrm{2D}}^{\mathrm{p}})^{2}}{E_{\mathrm{g}}^{2}}
\end{aligned}
\end{equation}
where $n_{\mathrm{2D}} =n_{\mathrm{3D}} L$ is the 2D number density of
valence electrons and
$\omega_{\mathrm{2D}}^{p}=\omega_{\mathrm{3D}}^{p}\sqrt{L}$ is the 2D
plasma frequency at static limit \cite{Nazarov_2015_2D_3D}, as
discussed in the main text. Apparently $n_{\mathrm{2D}}$ and
$\omega_{\mathrm{2D}}^{p}$ defines the superlattice-independent 2D
quantity $\alpha_{\mathrm{2D}}^{\parallel}$, while its 3D counterpart
$\varepsilon_{\mathrm{3D}}$ is dependent on $L$. By defining the 2D
valence charge density
$\sigma_{\mathrm{2D}}^{\mathrm{v}}=n_{\mathrm{2D}}e$, we have also
calculated $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
$\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the C2DB database, as shown in Figure \ref{fig:plasma}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.65\linewidth]{img/SI-lorentz-model.pdf}
  \caption{Calculated$\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
    $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the
    C2DB database. The broken line shows the theoretical prediction
    from single-oscillator model.}
  \label{fig:plasma}
\end{figure}
It can be seen that, a large number of materials are close to the
theoretical value of
$\alpha_{\mathrm{2D}}^{\parallel} = \frac{e^{2} n_{\mathrm{3D}} L}{m_{e}
  E_{\mathrm{g}}^{2}}$ (broken line). However there are also many
violations to this simple relation, making such model not suitable for
quantitative prediction of the 2D dielectric nature, due to the
oversimplification of single Lorentz oscillator. Nevertheless, this
example shows excellently how the quantities in both dimensions are
related to each other.

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
  \caption{Validation the linear relation between \textbf{a}
    $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$
    and \textbf{b}
    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB
    2D material database, corresponding to Figure \ref{main-fig-3}c
    and \ref{main-fig-3}d in main text.}
  \label{fig:gpaw-alpha-relation}
\end{figure}

@@

A common approach for describing the bulk dielectric function of bulk
semiconductors is via the Lorentz oscillator model, where the
dielectric function is dominated by the plasma frequencies
$\omega_{\mathrm{3D}}^{\mathrm{p}}$ and bandgap $E_{\mathrm{g}}$ of
individual oscillators \cite{ketterson_physics_2016}. At zero optical
frequency and the static limit, the dielectric constant for single
oscillator is:
\begin{equation}
  \label{eq:eps-plas-3D}
  \varepsilon_{\mathrm{3D}} = 1 +
  \frac{\hbar^{2} (\omega_{\mathrm{3D}}^{\mathrm{p}})^{2}}{E_{\mathrm{g}}^{2}}
\end{equation}
where
$\omega_{\mathrm{3D}}^{\mathrm{p}} = {\displaystyle \sqrt{\frac{e^{2}
      n_{\mathrm{3D}}}{\varepsilon_{0} m_{e}}}}$, where
$n_{\mathrm{3D}}$ is the 3D number density of valence
electrons. Combine Eq. \ref{eq:eps-plas-3D} with main text
Eq. \ref{main-eq:alpha-para-def}, we get:
\begin{equation}
  \begin{aligned}
  \label{eq:alpha-plas}
  \alpha_{\mathrm{2D}}^{\parallel} &= \frac{e^{2} n_{\mathrm{3D}} L}{m_{e} E_{\mathrm{g}}^{2}} \\
  &= \frac{e^{2} n_{\mathrm{2D}}}{m_{e} E_{\mathrm{g}}^{2}} \\
  &= \varepsilon_{0} \frac{\hbar^{2}
    (\omega_{\mathrm{2D}}^{\mathrm{p}})^{2}}{E_{\mathrm{g}}^{2}}
\end{aligned}
\end{equation}
where $n_{\mathrm{2D}} =n_{\mathrm{3D}} L$ is the 2D number density of
valence electrons and
$\omega_{\mathrm{2D}}^{p}=\omega_{\mathrm{3D}}^{p}\sqrt{L}$ is the 2D
plasma frequency at static limit \cite{Nazarov_2015_2D_3D}, as
discussed in the main text. Apparently $n_{\mathrm{2D}}$ and
$\omega_{\mathrm{2D}}^{p}$ defines the superlattice-independent 2D
quantity $\alpha_{\mathrm{2D}}^{\parallel}$, while its 3D counterpart
$\varepsilon_{\mathrm{3D}}$ is dependent on $L$. By defining the 2D
valence charge density
$\sigma_{\mathrm{2D}}^{\mathrm{v}}=n_{\mathrm{2D}}e$, we have also
calculated $\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
$\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the C2DB database, as shown in Figure \ref{fig:plasma}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.65\linewidth]{img/SI-lorentz-model.pdf}
  \caption{Calculated$\alpha_{\mathrm{2D}}^{\parallel}$ as a function of
    $\sigma_{\mathrm{2D}}^{\mathrm{v}}/E_{\mathrm{g}}^{2}$ using the
    C2DB database. The broken line shows the theoretical prediction
    from single-oscillator model.}
  \label{fig:plasma}
\end{figure}
It can be seen that, a large number of materials are close to the
theoretical value of
$\alpha_{\mathrm{2D}}^{\parallel} = \frac{e^{2} n_{\mathrm{3D}} L}{m_{e}
  E_{\mathrm{g}}^{2}}$ (broken line). However there are also many
violations to this simple relation, making such model not suitable for
quantitative prediction of the 2D dielectric nature, due to the
oversimplification of single Lorentz oscillator. Nevertheless, this
example shows excellently how the quantities in both dimensions are
related to each other.
